---
title       : Simulation of die rolls
subtitle    : 
author      : Daniel Jungen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

When rolling an ordinary die the result is one of the numbers 1 to 6. This can be simulated in R using the following code:

```{r}
sample(1:6, 1, replace = TRUE)
```

From a mathematical point of view this can be modelled as an Laplace-experiment. That means that the probability of getting a certain given number out of that roll is 1/6.

The more often we roll the die the more uniformly will be the outcome, i.e. if you roll a die several thousand times, it is very likely to have more or less the same number of outcomes for ever number from 1 to 6.

---


## More than just 6 sides

The RPG-players know that there are not just dice with 6 faces but also dice with 20 or more faces

In that case the statements from the previous slide hold but of course with 1/s and 1 to s respectively where s denotes the number of faces of a die.

So a simulation of several die rolls of a die with s faces can be simulated in R by the following code:


```{r}
n=20 #number of rolls
f=10 #number of faces of the die

sample(1:f, n, replace = TRUE)
```


---

## A shiny app

Under https://danielac.shinyapps.io/DataProdWeek4/ there is a nice little shiny app which allows the user to set a number of die rolls as well as a number of faces of a die and the result is a histogram of the distribution of the outcome

It allows the user to play around with the distributions and see that the distribution of the outcome gets more and more uniform as n grows larger.

---

## Where to find what

The app can be found under the link on the previous page.

The code for the program can be found in the github repo https://github.com/mrdjv2/DataProdWeek4.

In the subdirectory "pitch" there is the code for that file as well as the html-file itself.


